A Survey of Sterile Neutrinos

### 2015-04-14 p3_505/paper/paper3.tex
matts changes
small changes

The systematics of the MiniBooNE detector made it difficult to differentiate between $\pi^0 \rightarrow \gamma\gamma$ and an electron in the detector; therefore, there is a large uncertainty in the total number of $\overline{\nu}_e$ events. It is also hypothesized that the neutrino flux from the Booster neutrino beam must be studied more rigorously.
\subsection{Reactor Anomaly}
There has been an effort to re-analyse short baseline reactor neutrino oscillation data using newer flux calculations. These calculations show the posibility of the disappearane of reactor $\overline{\nu}_e$.
\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{../figures/reactor_anom.png}
  \caption{Plot for the short baseline reactor antineutrino anomaly. The red curve shows a possible three active neutrino mixing solution, using $\sin^2\theta_{13} = 0.06$. The blue curve shows a possible solution including a new neutrino mass state with $\Delta m^2 \gg 1\text{ eV}^2$.}
\end{figure}

@@

@@

@@

\section{Conclusions}
xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx
who cares

>>>>

The systematics of the MiniBooNE detector made it difficult to differentiate between $\pi^0 \rightarrow \gamma\gamma$ and an electron in the detector; therefore, there is a large uncertainty in the total number of $\overline{\nu}_e$ events. It is also hypothesized that the neutrino flux from the Booster neutrino beam must be studied more rigorously.
\subsection{Reactor Anomaly}
There has been an effort to re-analyse short baseline reactor neutrino oscillation data using newer flux calculations. These calculations show the possibility of the disappearance of reactor $\overline{\nu}_e$.
\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{../figures/reactor_anom.png}
  \caption{Plot for the short baseline reactor antineutrino anomaly. The red curve shows a possible three active neutrino mixing solution, using $\sin^2\theta_{13} = 0.06$. The blue curve shows a possible solution including a new neutrino mass state with $\Delta m^2 \gg 1\text{ eV}^2$.}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[width=1\columnwidth]{../figures/sk1.pdf}
 \caption{Super-Kamiokande sterile neutrino exclusion limits~\cite{SuperK}. TODODESCRIPTIONHERE}
 \label{fig:SuperK}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[width=1\columnwidth]{../figures/daya1.pdf}
 \caption{Daya Bay sterile neutrino exclusion limits~\cite{DayaBay}. TODODESCRIPTIONHERE}
 \label{fig:DayaBay}
\end{figure}

@@

\section{Conclusions}
xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx xxxxxxxx xxxxxx
